Galois Slicing as Differentiation

### 2025-07-11 main/definability.tex
Delete last sentence.
[ tex ] reword Thm 5.3

\begin{theorem}
  \label{thm:underlying-interp-equal} For all
  $\Gamma \vdash M : \tau$, where $\Gamma$ and $\tau$ are first-order,
  the interpretation $\sem{\Gamma \vdash M : \tau}_{\Set}$ in $\Set$
  and the interpretation
  $\sem{\Gamma \vdash M : \tau}_{\Fam(\MeetSLat \times
    \JoinSLat^\op)}$ agree on their first components.
\end{theorem}

\begin{proof}
  Instantiate \thmref{glr-definability} with the functor
  $\langle \mathrm{Id} , \pi_1 \rangle : \Fam(\MeetSLat \times
  \JoinSLat^\op) \to \Fam(\MeetSLat \times \JoinSLat^\op) \times \Set$
  that is the identity in the first component and projects out the
  underlying function in the second. We get, for each
  $\Gamma \vdash M : \tau$, a $g$ such that
  $g = \sem{\Gamma \vdash M : \tau}_{\Fam(\MeetSLat \times
    \JoinSLat^\op)}$ and
  $\pi_1(g) = \sem{\Gamma \vdash M : \tau}_\Set$. Therefore,
  $\pi_1(\sem{\Gamma \vdash M : \tau}_{\Fam(\MeetSLat \times
    \JoinSLat^\op)}) = \sem{\Gamma \vdash M : \tau}_\Set$.
\end{proof}

>>>>

\begin{theorem}
  \label{thm:underlying-interp-equal} For all
  $\Gamma \vdash M : \tau$, where $\Gamma$ and $\tau$ are first-order,
  the underlying function in the interpretation
  $\sem{\Gamma \vdash M : \tau}_{\Fam(\MeetSLat \times
    \JoinSLat^\op)}$ is equal to the interpretation
  $\sem{\Gamma \vdash M : \tau}_{\Set}$ in $\Set$.
\end{theorem}

\begin{proof}
  Instantiate \thmref{glr-definability} with the functor
  $\langle \mathrm{Id} , \pi_1 \rangle : \Fam(\MeetSLat \times
  \JoinSLat^\op) \to \Fam(\MeetSLat \times \JoinSLat^\op) \times \Set$
  that is the identity in the first component and projects out the
  underlying function in the second. For each
  $\Gamma \vdash M : \tau$, we obtain a $g$ such that
  $g = \sem{\Gamma \vdash M : \tau}_{\Fam(\MeetSLat \times
    \JoinSLat^\op)}$ and
  $\pi_1(g) = \sem{\Gamma \vdash M : \tau}_\Set$. Substituting $g$
  yields the result.
\end{proof}
